Between-dataset comparisons

### 2019-11-15 analysis/reports/cross_dataset.Rmd
add summary plots and set up to run all of fia

* FIA really struggles to get 2500 samples
* Portal is the *most* concentrated of all the datasets.
* Then MCDB and misc, then gentry, then bbs. FIA is hard to place but looks idiosyncratic.
* Curious about how variation in %ile maps on to S and N, *particularly* for Gentry and BBS. 
* Skewness is less extreme than Simpson (more density in the in-between). 
* Singletons doesn't appear to be terrifically impactful. From now on filtering to *unaltered* vectors.

```{r s and n mapping, fig.width = 12, fig.height = 10}

@@

skew_s_n_maps <- ggplot(data = all_di, aes(x = s0, y = n0, color = skew_percentile)) +
  geom_point(alpha = .3) +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free") + 
  ggtitle("Skewness") +
  scale_color_viridis_c(option = "plasma", end= .75)

@@

simpson_s_n_maps <- ggplot(data = all_di, aes(x = s0, y = n0, color = simpson_percentile)) +
  geom_point(alpha = .3) +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free") + 
  ggtitle("Simpson") +
  scale_color_viridis_c(option = "plasma", end= .75, direction = -1)

>>>>

* FIA really struggles to get 2500 samples
* Portal is the *most* concentrated of all the datasets.
* Then MCDB and misc, then gentry, then bbs. FIA is hard to place but looks idiosyncratic.
* Curious about how variation in %ile maps on to S and N, *particularly* for Gentry and BBS. 
* Skewness is less extreme than Simpson (more density in the in-between). 
* Singletons doesn't appear to be terrifically impactful. From now on filtering to *unaltered* vectors.
* I think it's best to filter to at least 2000 samples.

Some summary statistics:
```{r summary stats}

di_summary <- all_di %>%
  filter(nsamples >= 2000) %>%
  group_by(dat, singletons) %>%
  summarize(mean_skew = mean(skew_percentile, na.rm=T),
            sd_skew = sd(skew_percentile, na.rm = T),
            mean_simpson = mean(simpson_percentile, na.rm = T),
            sd_simpson = sd(simpson_percentile, na.rm = T),
            mean_nsamples = mean(nsamples),
            nsites = length(unique(site))) %>%
  ungroup()

skew_summary_plot <- ggplot(data = di_summary, aes(x = singletons, y = mean_skew, group = singletons)) +
  geom_point() +
  geom_errorbar(aes(x = singletons, ymin = mean_skew - sd_skew, ymax = mean_skew + sd_skew)) +
  geom_label(aes(x = singletons, y = 10, label = signif(mean_skew, digits = 4))) +
  theme_bw() +
  facet_wrap(vars(dat)) +
  geom_hline(yintercept = 100, linetype = 2, color = "red") +
  ylim(0, 110) +
  ggtitle("Skewness, >= 2000 samples")
skew_summary_plot

simpson_summary_plot <- ggplot(data = di_summary, aes(x = singletons, y = mean_simpson, group = singletons)) +
  geom_point() +
  geom_errorbar(aes(x = singletons, ymin = mean_simpson - sd_simpson, ymax = mean_simpson + sd_simpson)) +
    geom_label(aes(x = singletons, y = 90, label = signif(mean_simpson, digits = 4))) +
  theme_bw() +
  facet_wrap(vars(dat)) +
  geom_hline(yintercept = 0, linetype = 2, color = "red") +
  ylim(-10, 100) +
  ggtitle("Simpson's, >= 2000 samples")
simpson_summary_plot

```{r s and n mapping, fig.width = 12, fig.height = 18}

@@

skew_s_n_maps <- ggplot(data = all_di, aes(x = s0, y = n0, color = skew_percentile)) +
  geom_point(alpha = .1, size = .5) +
  geom_point(data = filter(all_di, nsamples >= 2000), alpha = .2) +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free", ncol = 2) + 
  ggtitle("Skewness") +
  scale_color_viridis_c(option = "plasma", end= .75)

@@

simpson_s_n_maps <- ggplot(data = all_di, aes(x = s0, y = n0, color = simpson_percentile)) +
  geom_point(alpha =  .1, size = .5) +
  geom_point(data = filter(all_di, nsamples >= 2000), alpha = .2) +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free", ncol = 2)  + 
  ggtitle("Simpson") +
  scale_color_viridis_c(option = "plasma", end= .75, direction = -1)
